%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee
% that it will correctly compile on your system if you have a non-standard
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%
% Forked by Stas Sușcov (stas@nerd.ro)
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, a4paper]{article}
\usepackage{fontspec}

% DOCUMENT LAYOUT
\usepackage{geometry}
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\usepackage[usenames,dvipsnames]{color}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont[
        Ligatures={Common},
        Numbers={OldStyle}
]{Source Serif Pro Light}
\setmonofont{Source Serif Pro Light}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty}
\usepackage[normalem]{ulem}
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize}
\subsubsectionfont{\mdseries\upshape\large}

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[
        dvipdfm, bookmarks, colorlinks, breaklinks,
% ---- FILL IN HERE THE TITLE AND AUTHOR
        pdftitle={Stas Sușcov Résumé}, pdfauthor={Stas Sușcov},
        pdfproducer={http://nitens.org/taraborelli/cvtex}
]{hyperref}
\hypersetup{
        linkcolor=RoyalPurple,
        citecolor=RoyalPurple,
        filecolor=black,
        urlcolor=RoyalPurple
}

% DOCUMENT
\begin{document}

{\LARGE Stas Sușcov}
\\[1cm]
Cluj-Napoca, Transylvania
\\[.2cm]
\href{mailto:stas@nerd.ro}{stas@nerd.ro},
\href{http://stas.nerd.ro/}{http://stas.nerd.ro},
\href{http://ampersate.com/}{http://ampersate.com}
\\[.2cm]
\texttt{(+40) 76-56-55-963}
% \vfill

%%\hrule
\section*{Spoken Languages}
Romanian, English, Ukrainian, Russian

%\hrule
\section*{Education}
\noindent
\years{2010-2016}\textsc{Computer Science} at „Babeș-Bolyai” University from Cluj-Napoca, Romania\\
\years{2009}\textsc{Computer Science} at „Lucian Blaga” University from Sibiu, Romania\\
\years{2007-2010}\textsc{Computer Science} at Technical University of Cluj-Napoca, Romania\\
\years{2003-2007}\textsc{Mathematics and Informatics} at „Axente-Sever” Highschool, Mediaș, Romania

%\hrule
\section*{Professional Experience}

\years{2014-2016}Lead Developer at Flavma Inc. • \emph{\href{http://flavma.com}{Flavma.com}}
\\
\begin{footnotesize}
One of the first technical employees. I led the technical decisions, ops and
team development helping the company grow from 7 to 30+ employees.
One of the major challenges was to build the data processing pipeline for our
vendor integrations (over 5k files per day, resulting in gigabytes of data to
process) with post processing and data mining operations.
I also led the devops where one of the biggest challenge was to scale our
customer base while keeping the infrastructure expenses at minimum.
\end{footnotesize}
\\[.2cm]

\years{2013-2014}Cofounder of the Founden • \emph{\href{https://github.com/Founden}{Founden.com}}
\\
\begin{footnotesize}
Technical lead, helped build a new team. We iterated through over 4 prototypes
in less than a year. Due to lack of further funding we decided to open source
all of our work. The story of this venture is available on
\href{http://ampersate.com/the-last-7-months-of-our-venture}{ampersate.com}.
\end{footnotesize}
\\[.2cm]

\years{2012-2013}Cofounder of the Courseware Project • \emph{\href{http://coursewa.re}{Coursewa.re}}
\\
\begin{footnotesize}
One of the startups I bootstrapped. After working for two years on the Google
Summer Of Code scholarships for an e-learning project, I decided to build a
SaaS product. Courseware is a SaaS for everyone who wants to start a virtual
classroom, with: courses, grades, attendance, assessments and certificates. Due
to lack of cash and one of the founders leaving the project, I decided to close
it and open-source everything. Courseware is one of my favorite projects.
You can read the full story on
\href{http://ampersate.com/moving-on}{ampersate.com}.
\end{footnotesize}
\\[.2cm]

\years{2012 Autumn}Web Operations at AppThemes • \emph{\href{http://appthemes.com/about}{AppThemes.com}}
\\
\begin{footnotesize}
Led the migration of the whole infrastructure into cloud (Linode).
Configurations management with SaltStack. CI and CD with Jenkins with
production and staging application servers and master-slave databases.
Most of the project sources are now
\href{https://github.com/AppThemes/salt-config-example}{open source}.
\end{footnotesize}
\\[.2cm]

\years{2012 Autumn}Consultant for Licensecompanion, Inc. • \emph{\href{http://www.licensecompanion.com/}{LicenseCompanion.com}}
\\
\begin{footnotesize}
Ember.js consulting and development for a search engine application to work
with Solr.
\end{footnotesize}
\\[.2cm]

\years{2012 Summer}Software Developer at SkinVision • \emph{\href{http://skinvision.com}{SkinVision.com}}
\\
\begin{footnotesize}
Skin cancer detection and monitoring software.
Our team built and scaled the web services including image processing API.
We also automated the UV index tracker (handling dozens of gigabytes of data).
\end{footnotesize}
\\[.2cm]

\years{2012 Spring}Software Developer at ProAtria Ltd. • \emph{\href{https://www.sftpplus.com/}{SFTPPlus}}
\\
\begin{footnotesize}
Enterprise grade file transfer software solutions written in Python (Twisted).
One of my responsibilities was to add the centralised logging (primarily for
SQLite, but not only) and build a web client prototype for the administration
panel.
\end{footnotesize}
\\[.2cm]

\years{2011-2013}Cofounder of Risktronics/Circularia • \emph{\href{http://circularia.com}{Circularia.com}}
\\
\begin{footnotesize}
Fintech software as a service based on the concept of rotating savings and
credit association. Self bootstrapped, now defunct.
\end{footnotesize}
\\[.2cm]

\years{2010-2011}Consultant at \emph{Inform Media}
\\
\begin{footnotesize}
Media and publishing software solutions.
Helped train and migrate existing closed source solutions to
WordPress and other open source technologies.
\end{footnotesize}
\\[.2cm]

\years{2010}Member of the \emph{Ubuntu Website Team} • \emph{\href{https://launchpad.net/~ubuntu-website}{Launchpad.net}}
\\
\begin{footnotesize}
Initiator and author of the WordPress-LoCo project used by official and local
communities to build web resources following Ubuntu guidelines.  Created a
facebook application that will allow users to place Ubuntu Countdown Banners on
their profile pages.
\end{footnotesize}
\\[.2cm]

\years{2010, 2011}Web Developer at \emph{Google Summer of Code} • \emph{\href{http://buddypress.coursewa.re/}{BuddyPress.Coursewa.re}}
\\
\begin{footnotesize}
Accepted as a student for \href{http://buddypress.org}{BuddyPress project}
under \href{http://wordpressfoundation.org/}{WordPress Foundation}.  Mentored
by John James Jacoby and \href{http://scholarpress.net}{ScholarPress} fellows:
Boone Gorges and Jeremy Boggs.  The project objective was to implement the
first learning management system over a social network.
\end{footnotesize}
\\[.2cm]

\years{2009-2012}Network Administrator at \emph{Pop F. Ioan Law Bureau}
\\
\begin{footnotesize}
GNU/Linux solutions consulting. Helped switch over to open source solutions
saving thousands of dollars.
\end{footnotesize}
\\[.2cm]

\years{2009}Consultant at \emph{Orpheus Capitals} • \emph{\href{http://www.orpheusindices.com/}{OrpheusIndices.com}}
\\
\begin{footnotesize}
Led the team responsible for building a centralised database of historical
stock market indices for US, India and Romania regions.
Syncing operations resulted in hundreds of gigabytes of indexed and searchable
data.
\end{footnotesize}
\\[.2cm]

\years{2008-2010}Software Developer and DevOps at \emph{Technical University of Cluj-Napoca} • \emph{\href{http://cc.utcluj.ro/}{CC.UTCluj.ro}}
\\
\begin{footnotesize}
One of the maintainers of the web, database, directory service, mail servers
and firewall services.
Led the campus hostel \#7 network administration and architecture.
Network administration using Allied Telesis and Cisco network equipment.
GNU/Linux and FreeBSD administration and container based solutions (OpenVZ,
FreeBSD Jails).
Backup systems deployments and OpenSolaris/FreeBSD (ZFS) and
GNU/Linux (RAID/LVM) based file servers.
One of the maintainers of the 2nd romanian FreeBSD mirror ---
\href{http://freebsd.utcluj.ro}{freebsd.utcluj.ro}\\
Led the team responsible for the rewrite of the intranet web resources related
to student services and federated WiFi authentication services.
\href{http://github.com/stas/student.utcluj.ro}{Student services codebase}.
\href{http://github.com/stas/eduroam-db}{WiFi services codebase}.
\end{footnotesize}
\\[.2cm]

\years{2008-2009}Web Operations at \emph{LiberTV}
\\
\begin{footnotesize}
Helped build the next version of one of the first P2P BitTorrent media
distribution platform. Project is now defunct and was open sourced due to
lack of funding.
\end{footnotesize}
\\[.2cm]

\years{2007}Web Developer at \emph{Mediaș City Hall} • \emph{\href{http://www.primariamedias.ro/}{PrimariaMedias.ro}}
\\
\begin{footnotesize}
While in high school, I won the contest to lead the rewrite of the Mediaș City
Hall website. One of the challenges was to handle the archives by migrating
hundreds of posts and pages from from Typo3 CMF to WordPress and securing the
web services.
\end{footnotesize}

\section*{Affiliations}

Free Software Group --- \href{http://softwareliber.ro}{softwareliber.ro}\\
Ubuntu Romanian Community --- \href{http://ubuntu.ro}{ubuntu.ro}\\
Open source contributions on Launchpad --- \href{http://launchpad.net/~sushkov}{Launchpad.net/~sushkov}\\
Open source contributions on GitHub --- \href{http://github.com/stas/}{github.com/stas}\\
Cluj-Napoca Linux User Group member --- \href{https://groups.google.com/d/forum/cjlug}{CJLUG on Google Groups} \\
Sibiu Linux User Group (now defunct) --- \href{http://sblug.ro}{sblug.ro}\\
GeekMeet --- \href{http://geekmeet.ro}{geekmeet.ro}\\
WordCamp --- \href{http://wordcamp.ro}{wordcamp.ro}\\
Former WordPress Romanian Localization Team coordinator --- \href{http://ro.wordpress.org}{ro.wordpress.org}\\
WordCamp Transilvania --- \href{https://2013.transylvania.wordcamp.org/}{2013.transylvania.wordcamp.org}\\
RailsGirls Cluj-Napoca (2014) --- \href{http://railsgirls.com/cluj}{railsgirls.com/cluj}

%\vspace{1cm}
\vfill{}
%\hrulefill

\begin{center}
{\scriptsize  Last updated: \today\- •\-
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
Typeset in \href{http://nitens.org/taraborelli/cvtex}{\fontspec{Source Serif Pro}\XeTeX }\\
% ---- FILL IN THE FULL URL TO YOUR CV HERE
\href{https://github.com/stas/stas.github.com/commits/resume}{Source code on GitHub}
}
\end{center}

\end{document}
